Blame and Coercion: Together Again for the Second Time

### 2019-10-17 paper.tex
minor fix

\newcommand{\eOOcast}[2]{#1 \langle #2 \rangle}

@@

\subsection{Cast Calculi}
\label{sec:cast-calculi}
\begin{figure}
	Syntax
	\[
	\begin{array}{rclr}
	\stxrule{T}{types}{
		\star \mid{}
		P
	}
	\stxrule{P}{pre-types}{
		\POOunit \mid
		\POOfun{T_1}{T_2} \mid
		\POOprod{T_1}{T_2} \mid
		\POOsum{T_1}{T_2}
	}
	\stxrule{c}{casts}{
		\cOOcast{T_1}{l}{T_2}
	}
	\stxrule{e}{terms}{
		\eOOvar{x} \mid{}
		\eOOsole{} \mid{}
		\eOOlam{T_1}{T_2}{x}{e} \mid
		\eOOapp{e_1}{e_2} \mid
		\eOOcons{e_1}{e_2} \mid
		\eOOcar{e} \mid
		\eOOcdr{e}
	}
	\stxrulecont{
		\eOOinl{e} \mid
		\eOOinr{e} \mid
		\eOOcase{e_1}{e_2}{e_3} \mid
		\eOOcast{e}{c} \mid
		\eOOblame{l}
	}
	\stxrule{v}{values}{
		\vOOtt{} \mid
		\vOOfun{\rho}{x}{e} \mid
		\vOOcons{v_1}{v_2} \mid
		\vOOinl{v} \mid
		\vOOinr{v} \mid		
		\vOOcast{v}{c}
	}
	\stxrule{I}{injectable types (\lazyD)}{
		P
	}
	\stxrule{I}{injectable types (\lazyUD)}{
		\POOunit \mid
		\POOfun{\star}{\star} \mid
		\star \times \star \mid
		\star + \star
	}
	\stxrule{o}{observations}{
		\oOOinj \mid
		\oOOsole \mid
		\oOOfun \mid
		\oOOcons \mid
		\oOOinl \mid
		\oOOinr \mid
		\oOOblame{l}
	}
	\end{array}
	\]

@@

	Term typing
	\fbox{$ \judgetype{\Gamma}{e}{T} $}
	\begin{gather*}
		\inference{
			\Gamma \vdash e : T_1 & T_1 \sim T_2
		}{
			\judgetype{\Gamma}{\eOOcast{e}{\cOOcast{T_1}{l}{T_2}}}{T_2}
		} \quad
		\inference{
		}{
			\judgetype{\Gamma}{\eOOblame{l}}{T}
		}
	\end{gather*}

@@

	& \dots  \\
	\redrule{
		\sOOinspect{\eOOcast{e}{\cOOcast{T_1}{l}{T_2}}}{\rho}{\kappa}
	}{
		\sOOinspect{e}{\rho}{\langle\cOOcast{T_1}{l}{T_2}\rangle\kappa}
	}{}
	\redrule{
		\sOOreturn{v_1}{(\mathtt{app_2} \; \vOOcast{v_2}{
				\cOOcast{\POOfun{T_1}{T_2}}{l}{\POOfun{T_3}{T_4}}
			} \; \kappa)}
	}{
		\sOOreturn{v_1}{
			\langle\cOOcast{T_3}{l}{T_1}\rangle
			(\mathtt{app_2} \; v_2 \; 
			\langle\cOOcast{T_2}{l}{T_4}\rangle \kappa)}
	}{}

@@

Most existing proofs about cast calculi defines the dynamic semantics with 
reduction semantics. We use a CEK machine instead because one of us is more 
familiar with CEK machines, and that he believes CEK machines are more 
convenient because space-efficiency is about compressing continuations.
\todo[inline]{Explain why you are using a CEK machine instead of
	reduction semantics. -JS
        \\---\\Fixed -KC
        \\---\\
        Change ``one of us'' to ``first author''. -JS
}

@@

	Reduction \fbox{$ \judgeSreduce{C}{s}{s} $}
	\[
	\begin{array}{rclr}
	& \vdots \\
	\redruleS{
		\sOOinspect{(\eOOlam{T_1}{T_2}{x}{e})}{\rho}{\kappa}
	}{
		\sOOreturn{(\hcvOOfun{id(T_1)}{\rho}{x}{e}{id(T_2)})}{\kappa}
	}{}
	\redruleS{
		\sOOinspect{\eOOcast{e}{\cOOcast{T_1}{l}{T_2}}}{\rho}{\kappa}
	}{
		\sOOinspect{e}{\rho}{ext(cast(T_1,l,T_2),\kappa)}
	}{}
	\redruleS{
		\sOOinspect{(\eOOcons{e_1}{e_2})}{\rho}{\kappa}
	}{
		\sOOinspect{e_1}{\rho}{cont(\hckOOconsI{e_2}{\rho}{\kappa})}
	}{}
	\redruleS{
		\sOOreturn{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{(c,\hckOOappII{v}{\kappa})}
	}{
		\sOOinspect{e}{\rho[x:=v']}{ext(c_2,\kappa)}
	}{
		\\ & &
		\sidecond{applyCast(c_1,v) = \rOOsucc{v'}}
	}
	\redruleS{
		\sOOreturn{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{(c,\hckOOappII{v}{\kappa})}
	}{
		\sOOhalt{(\oOOblame{l})}
	}{
		\\ & &
		\sidecond{applyCast(c_1,v) = \rOOfail{l}}
	}
	\end{array}
	\]

>>>>

\newcommand{\eOOcast}[4]{#1 \langle \cOOcast{#2}{#3}{#4} \rangle}

@@

\subsection{Cast Calculi}
\label{sec:cast-calculi}
\begin{figure}
	Syntax
	\[
	\begin{array}{rclr}
	\stxrule{T}{types}{
		\star \mid{}
		P
	}
	\stxrule{P}{pre-types}{
		\POOunit \mid
		\POOfun{T_1}{T_2} \mid
		\POOprod{T_1}{T_2} \mid
		\POOsum{T_1}{T_2}
	}
	\stxrule{e}{terms}{
		\eOOvar{x} \mid{}
		\eOOsole{} \mid{}
		\eOOlam{T_1}{T_2}{x}{e} \mid
		\eOOapp{e_1}{e_2} \mid
		\eOOcons{e_1}{e_2} \mid
		\eOOcar{e} \mid
		\eOOcdr{e}
	}
	\stxrulecont{
		\eOOinl{e} \mid
		\eOOinr{e} \mid
		\eOOcase{e_1}{e_2}{e_3} \mid
		\eOOcast{e}{T_1}{l}{T_2} \mid
		\eOOblame{l}
	}
	\stxrule{v}{values}{
		\vOOtt{} \mid
		\vOOfun{\rho}{x}{e} \mid
		\vOOcons{v_1}{v_2} \mid
		\vOOinl{v} \mid
		\vOOinr{v} \mid		
		\vOOcast{v}{c}
	}
	\stxrule{c}{casts}{
		\cOOcast{T_1}{l}{T_2}
	}
	\stxrule{I}{injectable types (\lazyD)}{
		P
	}
	\stxrule{I}{injectable types (\lazyUD)}{
		\POOunit \mid
		\POOfun{\star}{\star} \mid
		\star \times \star \mid
		\star + \star
	}
	\stxrule{o}{observations}{
		\oOOinj \mid
		\oOOsole \mid
		\oOOfun \mid
		\oOOcons \mid
		\oOOinl \mid
		\oOOinr \mid
		\oOOblame{l}
	}
	\end{array}
	\]

@@

	Term typing
	\fbox{$ \judgetype{\Gamma}{e}{T} $}
	\begin{gather*}
		\inference{
			\Gamma \vdash e : T_1 & T_1 \sim T_2
		}{
			\judgetype{\Gamma}{\eOOcast{e}{T_1}{l}{T_2}}{T_2}
		} \quad
		\inference{
		}{
			\judgetype{\Gamma}{\eOOblame{l}}{T}
		}
	\end{gather*}

@@

	& \dots  \\
	\redrule{
		\sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
	}{
		\sOOinspect{e}{\rho}{\langle\cOOcast{T_1}{l}{T_2}\rangle\kappa}
	}{}
	\redrule{
		\sOOreturn{v_1}{(\mathtt{app_2} \; \vOOcast{v_2}{
				\cOOcast{\POOfun{T_1}{T_2}}{l}{\POOfun{T_3}{T_4}}
			} \; \kappa)}
	}{
		\sOOreturn{v_1}{
			\langle\cOOcast{T_3}{l}{T_1}\rangle
			(\mathtt{app_2} \; v_2 \; 
			\langle\cOOcast{T_2}{l}{T_4}\rangle \kappa)}
	}{}

@@

Most existing proofs about cast calculi defines the dynamic semantics with 
reduction semantics. We use a CEK machine instead because the first author is 
more familiar with CEK machines, and that he believes CEK machines are more 
convenient because space-efficiency is about compressing continuations.
\todo[inline]{Explain why you are using a CEK machine instead of
	reduction semantics. -JS
        \\---\\Fixed -KC
        \\---\\
        Change ``one of us'' to ``first author''. -JS
 		\\---\\Fixed -KC
}

@@

	Reduction \fbox{$ \judgeSreduce{C}{s}{s} $}
	\[
	\begin{array}{rclr}
	& \vdots \\
	\redruleS{
		\sOOinspect{(\eOOlam{T_1}{T_2}{x}{e})}{\rho}{\kappa}
	}{
		\sOOreturn{(\hcvOOfun{id(T_1)}{\rho}{x}{e}{id(T_2)})}{\kappa}
	}{}
	\redruleS{
		\sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
	}{
		\sOOinspect{e}{\rho}{ext(cast(T_1,l,T_2),\kappa)}
	}{}
	\redruleS{
		\sOOinspect{(\eOOcons{e_1}{e_2})}{\rho}{\kappa}
	}{
		\sOOinspect{e_1}{\rho}{cont(\hckOOconsI{e_2}{\rho}{\kappa})}
	}{}
	\redruleS{
		\sOOreturn{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{(c,\hckOOappII{v}{\kappa})}
	}{
		\sOOinspect{e}{\rho[x:=v']}{ext(c_2,\kappa)}
	}{
		\\ & &
		\sidecond{applyCast(c_1,v) = \rOOsucc{v'}}
	}
	\redruleS{
		\sOOreturn{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{(c,\hckOOappII{v}{\kappa})}
	}{
		\sOOhalt{(\oOOblame{l})}
	}{
		\\ & &
		\sidecond{applyCast(c_1,v) = \rOOfail{l}}
	}
	\end{array}
	\]
